%!TEX root = main.tex
In our experiments we used the WMT12 \cite{WMT12} human evaluation data for Spanish-English systems. The data consists of $1141$ ranking annotations, in which each evaluator ranked %$5$ 
five out of the $12$ participating systems. \\
The annotation effort generated a total of $5705$ labels with an inter-annotator agreement of $\kappa=0.222$. Unfortunately, many of the translations have rankings coming from a single evaluator only. %, which means that from many sentences only 5 out of 12 systems were ranked. Therefore, to have more reliable data, we only included sentences for which there were at least $1.25$ labels per system. %More specifically, we discarded sentences with an average number of labels per system below $1.25$. 
In practical terms, this means that at least two evaluators had to evaluate the translations of the same source sentence, and 
%for a given source sentence with ranking evaluations by two different users, we required that 
at least two systems were ranked by both of those evaluators.
In the WMT12 data, a total of $923$ different source sentences were evaluated. % yet only $177$ had evaluations from more than $1$ judge. 
From these, we kept only the $155$ that complied with our requirement. 

\vspace{5pt}
To control for length (i.e number of words), we divided the sentences into three equally sized groups based on the sentence length of their reference translations.  Discarding the five longest ones the resulting sets \llong, \lmid, and \lshort averaged $30.88$, $18.18$, and $10.18$ words.
\vspace{5pt}

To have diversity in the quality of the translations, 
%we included translations of different levels of translation quality according to the human rankings. Therefore, 
we collected two translations per source sentence, one of superior quality (\qmax), and another one of inferior quality (\qmin). We measured quality 
%the \qmax and \qmin translations for each sentences 
according to the \emph{expected wins} \cite{WMT12}. In total, we used $300$ different translations.\footnote{For reproducibility, the full data matrix can be obtained at {https://github.com/Qatar-Computing-Research-Institute/wmt15eyetracking}}
\vspace{5pt}


